Factors Influencing Early Childhood Comprehension of American English with a Bayesian Model

### 2024-12-04 paper/paper.qmd
update final paper

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
library(here)
library(ggplot2)
library(modelsummary)
library(rstanarm)
library(arrow)
library(knitr)
library(kableExtra)
library(ggridges)
library(car)
library(broom.mixed)
```

@@

@@

We used the statistical programming language R [@citeR] to retrieve, simulate, clean, analyze, and test early childhood language comprehension data. The dataset used for this analysis is from the Wordbank database of children’s vocabulary growth [@citedata], specifically focusing on American English children. It contains comprehension and a variety of predictors, which include developmental, demographic, and environmental factors. Following the methodology discussed in “Telling Stories with Data” [@tellingstories], we 
discover how different predictors affect language comprehension in early childhood.

The dataset used in this study provides different data on the language comprehension skills of young children among American English language learners. The dataset consists of 14,826 rows and 22 columns covering a range of early childhood developmental attributes such as comprehension, output and parental education. To ensure the validity of the analysis, we filtered the data to include children whose comprehension assessments and caregiver information were complete, which would ensure a general, unbiased representation of the target population. This cleaning allowed us to focus on high-quality, well-integrated cases, which provided reliable results in young children's comprehension skills. For key operations, please refer to [Appendix -@sec-data-cleaning] for detailed data processing steps.

@@

## Outcome variables

@@

analysis_data <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))

@@

## Predictor variables
There are eight predictor variables for my study after cleaning. The Descriptions of Each Predictor Variable is in @tbl-Predictor shows at [Appendix -@sec-data-descriptions].

@@

## Model set-up

@@

## Model results and interpretation

@@

## Effect of birth order on language comprehension

@@

# CDI methodology overview and improvement

@@

## Target population, frame, and sample

@@

## Sample recruitment

@@

## Sampling approach and trade-offs

@@

## Non-response handling

@@

### Survey structure

**Survey introduction:**

@@

**Survey question:**

@@

## Model summary {#sec-model-summary}

@@

### Posterior predictive check

@@

\newpage
### Gelman-Rubin diagnosis

>>>>

```{r}
#| echo: false
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
library(ggplot2)
library(modelsummary)
library(rstanarm)
library(arrow)
library(knitr)
library(kableExtra)
library(ggridges)
library(car)
library(broom.mixed)

analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
```

@@

## Data Source
The dataset used for this analysis is from the World Database of Children’s Vocabulary Growth [@citedata], specifically focusing on American English children. The dataset used in this study provides different data on the language comprehension skills of young children among American English language learners. The original dataset consists of 14,826 rows and 22 columns covering a range of early childhood developmental variables such as comprehension, output and caregiver education.

@@

We used the statistical programming language R [@citeR] to retrieve, simulate, clean, analyze, and test early childhood language comprehension data. The dataset contains comprehension and a variety of predictors, which include developmental, demographic, and environmental factors. Following the methodology discussed in “Telling Stories with Data” [@tellingstories], we discover how different predictors affect language comprehension in early childhood.

To ensure the validity of the analysis, we filtered the original dataset to include children whose comprehension assessments and caregiver information were complete, which would ensure a general, unbiased representation of the target population. This cleaning allowed us to focus on high-quality, well-integrated cases, which provided reliable results in young children's comprehension skills. For key operations, please refer to [Appendix -@sec-data-cleaning] for detailed data processing steps.

@@

## Outcome Variables

@@

@@

## Predictor Variables
There are eight predictor variables for my study after cleaning. The Descriptions of Each Predictor Variable is in @tbl-Predictor shows at [Appendix -@sec-data-descriptions].

@@

## Model Set-up

@@

## Model Results and Interpretation

@@

## Effect of Birth Order on Language Comprehension

@@

# CDI Methodology Overview and Improvement

@@

## Target population, Frame, and Sample

@@

## Sample Recruitment

@@

## Sampling Approach and Trade-offs

@@

## Non-response Handling

@@

### Survey Structure

**Survey Introduction:**

@@

**Survey Question:**

@@

## Model Summary {#sec-model-summary}

@@

### Posterior Predictive Check

@@

\newpage
### Gelman-Rubin Diagnosis
